\section{SCRUM}
We used Pivotal Tracker as a tool for SCRUM.\\
For charts, select "CHARTS"\\
https://www.pivotaltracker.com/projects/678161\\

\subsection{Definition of Done}
We need to define when a story is done. We have chosen that a story can not be
marked as done before it fulfilled the following: \\
- Proper documentation has been written\\
- Tests have been written and they they must not fail\\
- New code must not break previously written tests\\

\subsection{The first Sprint}
Our sprints will be four week periods.\\
Scrum Team:\\
- Claus L. Henriksen (Development Team)\\
- Michael Søby Andersen (Development Team)\\
- Lasse Vork Borchet (Development Team)\\
- Kaj (Product Owner)\\
- Andrea (Scrum Master)\\
- Lotte (Development Team)\\
\\
\textbf{Sprint Goal}
The sprint is quiet long (four weeks).\\
We expect to write all the basic structure code for our system. These might be reviewed later on. The system will only work with a local iCal-file for now. \\
User interface is not a focus point in this sprint, but is merely for testing the functionality and feel of the system.\\
Multiple formats, remote communication, import and export features may be added in a later sprint.\\

\subsection{First Sprint Review}
\textbf{Meeting attendees}
Scrum Team:\\
- Claus L. Henriksen (Development Team)\\
- Michael Søby Andersen (Development Team)\\
- Lasse Vork Borchet (Development Team)\\
- Kaj (Product Owner)\\
- Andrea (Scrum Master)\\
- Lotte (Development Team)\\
No stakeholders attended.\\

%Referat?
\textbf{Meeting resume}
The planned stories for the sprint was finished within the sprint time limits. See https://www.pivotaltracker.com/projects/678161\\
The structure of the program seems solid, flexible and easy to maintain. No planned changes to this part.\\
The Controller took some effort, but otherwise this was an easy sprint. The upcoming sprints with GUI, remote communication and lots of tweaks are going to be more complicated.\\
We looked at the charts and we can see that deadlines were met.\\

Even though back end tweaks easily can be complicated, we expect to focus on the user interface in the next sprint. We would like to have some solid and usable designs to show the stakeholders at the next Sprint Review. This will also give us more time to redo the designs to meet the costumers wishes.\\

\subsection{First Sprint Retrospective}
The first Sprint Retrospective went well. It was an easy sprint, which was good because the Scrum Team has some new members, who needs time to adjust and to get used to PivotalTracker.\\
The first couple of Daily Scrum Meetings exceeded the usual 15 minutes, but this was expected due to the fact that we have a new member of the team.\\
\textbf{Improvements}
The Scrum Team has no improvement suggestions at this time.\\

\newpage